Modeling Interventions

### 2021-03-11 paper/paper.Rmd
small edits

These models also estimate a latent language ability for each child in the dataset. 
However, this ability is no doubt correlated with age, sex (females have larger vocabularies at young ages), and likely with features related to input quality. 
Estimating the contributions of these factors and determining whether/how language ability changes over developmental time is not possible with current datasets.
Thus, we conclude by discussing the next steps needed to test and build upon the standard model.

>>>>

These models also estimate a latent language ability for each child, but currently do not specify whether/how this value changes over time. 
However, this ability is no doubt correlated with age, as well as with features related to input quality. 
Estimating the contributions of these factors and determining whether/how language ability changes over developmental time is not possible with current datasets.
Thus, we conclude by discussing the next steps needed to test and build upon the standard model.
